---
title: "Jacci Ziebert"
output:
  pdf_document: default
  html_notebook: default
---

```{r Libraries}
library(ggplot2)
library(dplyr)
library(reshape2)
library(expss)
```

```{r Load files}
tweets <- readRDS("tweets_in_library_final_df.rds") %>%
  select( -c(2:3, 7:13, 32:33), -games.spec) %>% filter(X != 513)
# remove this game, wrong title

tweets_unique <- unique(tweets[, c(5, 7:21)]) # unique games - R loves to do fatal error here

api_mechanics <-  # Import ID codes for mechanics
  jsonlite::fromJSON( 
    "data/APImechanics.json") %>% as.data.frame() 
api_categories <- # Import ID codes for categories
  jsonlite::fromJSON( 
    "data/APIcategories.json") %>% as.data.frame() 
```

```{r Analysis of game length using Chi Sq}
tweets_game_count <- # First, get total counts (gcount) of games mentioned
  tweets %>% group_by(games.name) %>% summarise(gcount = n())

# Combine df to add 'gcount' column to unique games
tweets_unique <- left_join(tweets_unique, tweets_game_count, by = "games.name")

# Add game length category to unique games
tweets_unique <- tweets_unique %>% mutate(glength = cut(  
  games.max_playtime,
  c(0,
    30,
    60,
    90,
    120,
    500),
  labels = c(
    "Quick",
    "Short",
    "Medium",
    "Long",
    "Very long" #120-300 min
  ),
  include.lowest = F
))
# Make a table of count of game lengths by total game count and total reddit count
glength_reddit_tweets <- cbind(tweets = 
xtabs(tweets_unique$gcount~tweets_unique$glength), reddit = 
xtabs(tweets_unique$games.reddit_all_time_count~tweets_unique$glength))

chisq_glength <- chisq.test(x = glength_reddit_tweets[,'tweets'],
                            p = glength_reddit_tweets[,'reddit'], rescale.p=TRUE)
# rescale so reddit % equals 1

chisq_glength # accept that they are the same/similar
```
I did a Chi Squared GOF to test whether Twitter gamers are similar to Reddit gamers based on game length. I separated games into 5 categories by 30 minute intervals based on maximum play time.  With a null hypothesis the groups are similar (based on distrubtion of game lengths), I found that there is evidence to suggest Twitter and Reddit gamers share similar game length preferences. p-value is 0.2069.

```{r find popular game mechanics and game categories}
# First, I need to extract variables in the df; they're currently in list bc of JSON
gcategories <- unlist(tweets$games.categories) %>% as.data.frame()
gmechanics <- unlist(tweets$games.mechanics) %>% as.data.frame()   

#  Then I need to find what the category/mechanicss IDs mean
# So I join with the imported ID codes
tweets_mechanics <- left_join(gmechanics, api_mechanics, by = c("." = "mechanics.id")) 
tweets_categories <- left_join(gcategories, api_categories, by = c("." = "categories.id")) 

# This gives a count of each mechanic/category
tweets_mechanics <- tweets_mechanics %>% group_by(mechanics.name) %>% summarise(mechcount = n()) 
tweets_categories <- tweets_categories %>% group_by(categories.name) %>% summarise(catecount = n())
```
The rest of the code is making 4 bar charts
```{r Charts - Most popular games}
tweets_unique_top <- arrange(tweets_unique, desc(gcount)) %>% head(10L)

g_tweet_chart <-
      tweets_unique_top %>%
      ggplot(mapping = aes(x = reorder(games.name, desc(-gcount)), y = gcount)) +
      theme_classic() +
      geom_bar(fill = "#428BCA", position = 'dodge', stat = 'identity') +
      theme(axis.line=element_blank(),
            legend.position = "none",
            axis.ticks=element_blank(),
            axis.text.x = element_blank(),
            axis.text.y = element_text(size = 10, color = "black"),
            axis.title.y = element_blank(),
            plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 1),
            plot.background = element_rect(fill = "transparent", colour = NA),
            panel.background = element_rect(fill = "transparent")
      ) +
        scale_y_continuous(expand = expansion(mult = c(0, .05)), name = "") +
      labs(title = "Figure 1. Monopoly is the 3rd most Tweeted game") +
      geom_text(
        stat = 'identity',
        color = "white",
        size = 4,
        aes(label = gcount),
        fontface = "bold",
        hjust = 1.25
      ) +
      coord_flip()
ggsave("charts/tweet.png", plot = g_tweet_chart, width = 3.75, height = 4, units = "in")
```

```{r Charts - game mechanics}
tweets_mechanics_top <- arrange(tweets_mechanics, desc(mechcount)) %>% top_n(10) # take top 10 games

g_mech_chart <-
      tweets_mechanics_top %>%
      ggplot(mapping = aes(x = reorder(mechanics.name, desc(-mechcount)), y = mechcount)) +
      theme_classic() +
      geom_bar(fill = "#428BCA", position = 'dodge', stat = 'identity') +
      theme(axis.line=element_blank(),
            legend.position = "none",
            axis.ticks=element_blank(),
            axis.text.x = element_blank(),
            axis.text.y = element_text(size = 10, color = "black"),
            axis.title.y = element_blank(),
            plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 1),
            plot.background = element_rect(fill = "transparent", colour = NA),
            panel.background = element_rect(fill = "transparent")
      ) +
        scale_y_continuous(expand = expansion(mult = c(0, .05)), name = "") +
      labs(title = c(paste("Figure 4. Hand management is the top game mechanic", paste("\nTwitter gamers prefer")))) +
      # scale_y_continuous(expand = expansion(mult = c(0, .05)), name = "") +
      geom_text(
        stat = 'identity',
        color = "white",
        size = 4,
        aes(label = mechcount),
        fontface = "bold",
        hjust = 1.25
      ) +
      coord_flip()
ggsave("charts/mech.png", plot = g_mech_chart, width = 3.75, height = 4, units = "in")

```

```{r Charts - game categories}
tweets_categories_top <- arrange(tweets_categories, desc(catecount)) %>% top_n(10) # take top 10 games

g_cate_chart <-
      tweets_categories_top %>%
      ggplot(mapping = aes(x = reorder(categories.name, desc(-catecount)), y = catecount)) +
      theme_classic() +
      geom_bar(fill = "#428BCA", position = 'dodge', stat = 'identity') +
      theme(axis.line=element_blank(),
            legend.position = "none",
            axis.ticks=element_blank(),
            axis.text.x = element_blank(),
            axis.text.y = element_text(size = 10, color = "black"),
            axis.title.y = element_blank(),
            plot.title = element_text(size = 10, color = "black", face = "bold", hjust = 1),
            plot.background = element_rect(fill = "transparent", colour = NA),
            panel.background = element_rect(fill = "transparent")
      ) +
        scale_y_continuous(expand = expansion(mult = c(0, .05)), name = "") +
      labs(title = "Figure 3. What categories do Twitter gamers prefer?") +
      # scale_y_continuous(expand = expansion(mult = c(0, .05)), name = "") +
      geom_text(
        stat = 'identity',
        color = "white",
        size = 4,
        aes(label = catecount),
        fontface = "bold",
        hjust = 1.25
      ) +
      coord_flip()
ggsave("charts/cate.png", plot = g_cate_chart, width = 3.75, height = 4, units = "in")
```
```{r Charts - Chi-Square}
# These find the percent of total games by category for twitter/reddit
glength_percents <- glength_reddit_tweets %>% as.data.frame()
glength_percents$glen <- rownames(glength_percents)
glength_percents <- glength_percents %>%
  mutate(red_perc = reddit/sum(reddit),tweet_perc = tweets/sum(tweets))

glength_chart <- melt(glength_percents, id_vars = "leng") %>%
  filter(variable %in% c("tweet_perc","red_perc"))

chi_chart <-
      glength_chart %>%
      ggplot(mapping = aes(x = reorder(glen, desc(-value)), y = value, fill = variable)) +
      theme_classic() +
      geom_bar(position = 'dodge', stat = 'identity') +
      theme(axis.line=element_blank(),
            # legend.position = "none",
            axis.ticks=element_blank(),
            axis.text.x = element_blank(),
            axis.text.y = element_text(size = 10, color = "black"),
            axis.title.y = element_blank(),
            plot.title = element_text(size = 10, color = "black", face = "bold", hjust = .25),
            plot.background = element_rect(fill = "transparent", colour = NA),
            panel.background = element_rect(fill = "transparent")
      ) +
        scale_y_continuous(expand = expansion(mult = c(0, .05)), name = "") +
      labs(title = c(paste("Figure 2. Twitter and Reddit gamers share similar ", paste("\ngame preferences in game lengths")))) +
      geom_text(
        stat = 'identity',
        color = "white",
        size = 4,
        aes(label = scales::percent(value, accuracy = 2)),
        position = position_dodge(width =.9),
        fontface = "bold",
        hjust = 1.25
      ) +
      scale_fill_manual(
        name = "",
        values = c("red_perc" = "#D50032", "tweet_perc" = "#428BCA"),
        labels = c("Reddit", "Twitter")
      ) +
      coord_flip()
ggsave("charts/chi.png", plot = chi_chart, width = 3.75, height = 4, units = "in")
```


